Effective Reionization Likelihood from Planck 2018 Data (?)

### 2021-03-16 paper/rei.tex

\begin{figure}
\includegraphics[width=0.48\textwidth]
%{plots/pl18_pc_zmax30_pliklite_srollv2_1015_tau_posterior_fraccov_1p0_burnin_10000_yes_norm_gaussian0p1_0p12_0p14.pdf}
{paper/plots/pl18_tau_posterior_tanh.pdf}
\caption{Comparison of the total optical depth posterior for the tanh model in \refsec{example1} between the full Planck likelihoods (solid), our effective likelihood in the kernel density estimate mode with $f = 0.14$ (dotted), and in the Gaussian approximation mode (dashed) \ch{tune plot and line styles}. The KDE mode agree well with the full results, while giving a slightly broader posterior because the kernel density estimate in the PC space introduces smoothing at roughly $\sim$7\% level in the parameter posterior corresponding to $f = 0.14$. The Gaussian likelihood works well too, with no extra broadening of the posterior, but a negligible shift in the mean ($\sim XX\%$ of the error in $\tau$). This posterior is symmetric and does not capture the small skewness found in the full and KDE chains. \ch{might need to rephrase. \ch{This is plot is done. (might want to remove text label about zre, or add tanh in legend to mimick legend of Fig. 5)}}
}
\label{fig:tanh}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.48\textwidth]{paper/plots/pl18_taugtz_tanh_direct_vs_kde_vs_gaussian.pdf}
\caption{Comparison of the 68\% and 95\% C.L. constraints on the cumulative optical depth in the tanh model (described in \refsec{example1}) between the full Planck likelihoods (shaded bands), our effective likelihoods in the KDE mode (blue solid) and Gaussian mode (black dashed). The effective likelihoods results oscillate around zero at high-z because of the truncated representation of the models at 5 PCs (enough to represent any observable effects in the data). While the Gaussian approximation performs fairly well, the more complete KDE mode gives a slightly more accurate 95\% limits on the total optical depth.}
%double check plot, upper and lower limits seem to cross?
\label{fig:plot_taugtz_PC_vs_tanh}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.48\textwidth]
%normalized by area
%{results/tau_posterior_comparisons/pl18_tau_posterior_tanh_vs_tanh_kde_vs_tanh_gaussian_dz_auto_zre_prior_6p1_normalized_by_area.pdf}
%normalized by max
{results/tau_posterior_comparisons/pl18_tau_posterior_tanh_vs_tanh_kde_vs_tanh_gaussian_dz_auto_zre_prior_6p1_normalized_by_max.pdf}
\caption{Comparison of the total optical depth posterior for the tanh model in \refsec{example1} between the full Planck likelihoods (solid), our effective likelihood in the kernel density estimate mode with $f = 0.14$ (dotted), and in the Gaussian approximation mode (dashed) \ch{tune plot and line styles}. The KDE mode agree well with the full results, while giving a slightly broader posterior because the kernel density estimate in the PC space introduces smoothing at roughly $\sim$7\% level in the parameter posterior corresponding to $f = 0.14$. The Gaussian likelihood works well too, with no extra broadening of the posterior, but a negligible shift in the mean ($\sim XX\%$ of the error in $\tau$). This posterior is symmetric and does not capture the small skewness found in the full and KDE chains. \ch{might need to rephrase. \ch{This plot is done. Changed convention to normalization by max; to restore figure normalized by area, see comments in latex.}}
}
\label{fig:tanh}

\end{figure}
\begin{figure}[ht]
\includegraphics[width=0.48\textwidth]
%normalized by area
%{results/tau_posterior_comparisons/pl18_tau_posterior_tanh_vs_tanh_highz_vs_pc_dz_auto_zre_prior_6p1_normalized_by_area.pdf}
%normalized by max
{results/tau_posterior_comparisons/pl18_tau_posterior_tanh_vs_tanh_highz_vs_pc_dz_auto_zre_prior_6p1_normalized_by_max.pdf}
\caption{\ch{P(tau) PC (with and without prior) vs tanh vs tanh highz (normalized by max)}}
%double check plot, upper and lower limits seem to cross?
\label{fig:plot_tau_posterior_PC_vs_tanh_vs_tanh_highz}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.48\textwidth]{paper/plots/pl18_taugtz_tanh_direct_vs_kde_vs_gaussian.pdf}
\caption{Comparison of the 68\% and 95\% C.L. constraints on the cumulative optical depth in the tanh model (described in \refsec{example1}) between the full Planck likelihoods (shaded bands), our effective likelihoods in the KDE mode (blue solid) and Gaussian mode (black dashed). The effective likelihoods results oscillate around zero at high-z because of the truncated representation of the models at 5 PCs (enough to represent any observable effects in the data). While the Gaussian approximation performs fairly well, the more complete KDE mode gives a slightly more accurate 95\% limits on the total optical depth. \ch{add numbers in caption: 95\% (0.039, 0.02), best-fit (0.05290344, 0.005859431)}}
%double check plot, upper and lower limits seem to cross?
\label{fig:plot_taugtz_PC_vs_tanh}
\end{figure}
